### 2015-09-12 vmcai-2016-tex/lazy.tex
Some more changes

How the lazy
initialization is used is defined in \figref{fig:lazy}. Specifically,
the field-access rule in \figref{fig:lazy} uses initialization,
$\rightarrow_I^*$, to ensure the accessed field is
instantiated. Initialization in generalized symbolic execution never
happens for more than one object on any use of $\rightarrow_I^*$:
$\Lambda$ is either empty or contains exactly one location. The rest of the rules in \figref{fig:lazy} do not initialize, but they are included to elucidate how symbolic initialization differs from GSE with lazy initialization.

The $\rgse$ relation defined in \figref{fig:lazy} is a union over branching points on control flow
to support the final proof of the existence of a
bisimulation. Although it is apparent that there is non-determinism in
initialization, it is not the initialization where control flow
diverges in program execution. Rather, that occurs at branches and NULL-exceptions, and that is reflected in the composition of $\rgse$.

>>>>

How the lazy
initialization is used is defined in \figref{fig:lazy}. Specifically,
the field-access rule in \figref{fig:lazy} uses initialization,
$\rightarrow_I^*$, to ensure the accessed field is
instantiated. Initialization in generalized symbolic execution never
happens for more than one object on any use of $\rightarrow_I^*$:
$\Lambda$ is either empty or contains exactly one location. This property is an artifact of how GSE case spits when it instantiates: each choice is a new unique heap. The rest of the rules in \figref{fig:lazy} do not initialize, but they are included to elucidate how symbolic initialization differs from GSE with lazy initialization.

The $\rgse$ relation defined in \figref{fig:lazy} is a union over branching points on control flow
to support the final proof of the existence of a
bisimulation. Although it is apparent that there is non-determinism in
initialization at the first reference access partitioning the search space, control flow branches at comparisons and NULL-exceptions. This property is reflected in the composition of $\rgse$.

### 2015-09-12 vmcai-2016-tex/summary-heap.tex
Some more changes

\section{A Symbolic Heap}
A \emph{symbolic heap} is a tuple
$(\cfgnt{L}\ \cfgnt{R}\ \phi\ \eta)$, where the~\emph{location map}
$\cfgnt{L}$,~\emph{reference map} $\cfgnt{R}$, and~\emph{environment}
$\eta$ are partial functions, and the~\emph{path condition} $\phi$ is
a predicate over the program variables. Given reference $r$,
$\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is the guarded value set
in the heap associated with $r$. The constraint associated with each
location is a guard representing the conditions under which the
associated reference maps to the given location. By definition, any
location appears at most once in any given value set. Unions of value
sets containing the same location are resolved by forming a
disjunction of the constraints from each set. $\cfgnt{R}(\cfgnt{l},
\cfgnt{f}) = \cfgnt{r}$ is the reference associated with the given
location-field pair in the heap.

>>>>

\section{A Symbolic Heap}
A \emph{symbolic heap}, as defined in this work, is a tuple
$(\cfgnt{L}\ \cfgnt{R}\ \phi\ \eta)$, where the~\emph{location map}
$\cfgnt{L}$,~\emph{reference map} $\cfgnt{R}$, and~\emph{environment}
$\eta$ are partial functions, and the~\emph{path condition} $\phi$ is
a predicate over the program variables. Given reference $r$,
$\cfgnt{L}(r) = \{(\phi\ \cfgnt{l})\ ...\}$ is the guarded value set
in the heap associated with $r$. The constraint associated with each
location is a guard representing the conditions under which the
associated reference maps to the given location. By definition, any
location appears at most once in any given value set. Unions of value
sets containing the same location are resolved by forming a
disjunction of the constraints from each set. $\cfgnt{R}(\cfgnt{l},
\cfgnt{f}) = \cfgnt{r}$ is the reference associated with the given
location-field pair in the heap.
